### 2016-04-01 text/ms.Rmd
At a missing line

\noindent
**Acknowledgements**: We thank members of Phase I of the working group 'Developing new approaches to global stock status assessment and fishery production potential of the seas' who
contributed to developing the data-limited methods and simulations used in our
analysis.
We thank E. Jardim, F. Scott, and J.A. Hutchings for helpful comments during the development of this project, and R.D. Methot for comments on an earlier version of the manuscript.
We thank the Gordon and Betty Moore Foundation for funding the working group
'Applying data-limited stock status models and developing management guidance for unassessed fish stocks'.

>>>>

\noindent

**Acknowledgements**: We thank members of Phase I of the working group 'Developing new approaches to global stock status assessment and fishery production potential of the seas' who
contributed to developing the data-limited methods and simulations used in our
analysis.
We thank E. Jardim, F. Scott, and J.A. Hutchings for helpful comments during the development of this project, and R.D. Methot for comments on an earlier version of the manuscript.
We thank the Gordon and Betty Moore Foundation for funding the working group
'Applying data-limited stock status models and developing management guidance for unassessed fish stocks'.
